Supporting Information

### 2021-12-14 ms/ms.Rmd
biorxiv

*Mimulus cardinalis* ($=$*Erythranthe cardinalis* [@lowry_case_2019]) is a perennial forb native to the Western US (California and Oregon). It is predominantly outcrossing, self-compatible, hummingbird-pollinated. We used five focal populations from throughout the geographic range of *M. cardinalis* (Table \ref{tab:focal_pops}). These five focal populations are a subset of those we used previously to identify a cline in germination and other traits [@muir_grow_2017]. Seeds were collected in the field from mature, undehisced fruits left in open coin envelopes for 2-4 weeks to dry, then stored at room temperature. To control for maternal effects, we grew a large number of field-collected seeds in the greenhouse and generated seed families for this experiment by hand-pollinating individuals using the breeding design described in the next section.

@@

$$V_P = V_G + V_E$$
We did not have statistical power to estimate nonadditive genetic contributions, therefore we made the simplifying operational assumption that all genetic variance is additive. The broad-sense ($H^2$) heritability is the fraction of phenotypic variance contributed by additive genetic variance:

@@

## Estimating genetic variance in germination rate
The full germination-rate model included a fixed effect of population, fixed effect of cohort, a random effect of greenhouse block, and a random effect of parent as either dam or sire to estimate additive genetic variance. Most quantitative traits are modeled with a Gaussian (i.e. normal) distribution, but this is inappropriate for germination which has a lower bound at 0 and is censused at discrete time points. A Gaussian distribution might be an adequate approximation if the time to germination was longer and more spread out so that the effects of a zero lower bound and discrete sampling interval were inconsequential. However, given the rapid germination rate and small spread in timing for *M. cardinalis*, we used a different approach. Instead, we modeled genetic variation in a continuously distributed latent rate parameter that is measured as a discrete number of days to germination. Time to germination can be modeled similar to other waiting time or survival processes. There are several common waiting-time distributions with a lower bound at zero, but we used the log-normal distribution because unlike some other common distributions (e.g. exponential), the mean and variance of log-normal distribution are separate parameters. Hence, we can model the variance components separate from differences in the mean germination rate. We discretized the distribution using the definite integral of the probability density to calculate a probability mass. Let the probability density with parameters $\theta$ be $f(x|\theta)$. If a seed was censused to have germinated on day $i$, it could have germinated at any time between the previous census on day $t_{i-1}$. The associated probability mass $g(x|\theta)$ is:

@@

Phenotypic clines are often interpreted as evidence for local adaptation but evolutionary forces besides selection can also generate associations between phenotypes and environment [@endler_geographic_1977]. If genotypic selection measured under natural conditions favors local phenotypes, this supports the hypothesis that phenotypic clines are adaptive. Alternatively, failure to detect selection could indicate that nonadaptive evolutionary forces maintain phenotypic variation. We measured the effect of germination rate in the greenhouse, which varies clinally with latitude in *Mimulus cardinalis* [@muir_grow_2017], on early winter survival. Although there was genetic variation in germination rate within and between five populations (Table \ref{tab:focal_pops}; Table \ref{tab:vc_table_germ}; Fig. \ref{fig:mean-traits}a), there was no evidence selection consistently favored local genotypes. We predicted that earlier germination should be favored in the South garden and later germination favored in the North garden. Instead, in both North and South gardens, populations that germinated faster on average also had higher survival, though survival in the North garden was lower than the South overall (Fig. \ref{fig:selection}). Apparent selection for faster germination in both gardens is likely indirect rather than causal. Populations originating from the southern range limit survived more often and germinated faster. Within populations there was no genetic variance in winter survival despite genetic variance in germination rate, indicating that differences in germination rate are probably not the main cause of differences in winter survival. Our results are not consistent with selection on survival maintaining phenotypic clines in germination rate. Rather, the results may indicate a role for nonadaptive evolution in this and possibly other traits.

@@

## What maintains genetic variation in germination rate?
One possibility is that germination rate measured in the greenhouse is not representative of what occurs in nature. In the field, seeds may use additional cues such as day length or temperature that did not vary in our experiment. We may not be able to measure selection on variation in germination rate unless it occurs in the field. For example, seedlings in the north may require a longer duration of favorable conditions to ensure they do not germinate in late fall or during a brief warm period in early spring. Either scenario might cause them to be exposed to a hard, damaging frost. We may not be able to observe this type of selection without germinating plants in the field at different times of the season. Alternatively, variation may be the result of nonadaptive evolution. *M. cardinalis* has expanded its range northward most likely after the last glacial maximum [@sheth_demographic_2018]. Population expansion can lead to the accumulation of deleterious alleles because of stronger genetic drift [@peischl_accumulation_2013], serial founder events [@slatkin_serial_2012], and maladaptation [@polechova_is_2018]. If selection actually favors faster germination, the slower germination and lower survival of northern populations may both be caused by the accumulation of deleterious genetic variation at the expanding range margins. The current cline could also be a legacy of selection in the recent past which is now less strong or at least not observed during our study [@saccheri_selection_2008].

@@

The reciprocal transplant experiment did not support our hypothesis that local adaptation maintains clinal variation in germination rate in *M. cardinalis*. We cannot exclude the possibility that artificial aspects of our experimental design may have prevented us from measuring selection on germination rate realistically. It is also possible that climate anomalies during our experiment prevented us from observing historical patterns of selection that led to present-day phenotypic variation. It is plausible that the cline in germination rate and other phenotypes may be caused by nonadaptive forces that increase the frequency of deleterious alleles during range expansion. Studies like ours that combine clines with reciprocal transplants are necessary to determine what evolutionary forces shape range-wide phenotypic variation within species.

>>>>

*Mimulus cardinalis* ($=$*Erythranthe cardinalis* [@lowry_case_2019]) is a perennial forb native to the Western US (California and Oregon). It is predominantly outcrossing, self-compatible, and hummingbird-pollinated. We used five focal populations from throughout the geographic range of *M. cardinalis* (Table \ref{tab:focal_pops}). These five focal populations are a subset of those we used previously to identify a cline in germination and other traits [@muir_grow_2017]. Seeds were collected in the field from mature, undehisced fruits left in open coin envelopes for 2-4 weeks to dry, then stored at room temperature. To control for maternal effects, we grew a large number of field-collected seeds in the greenhouse and generated seed families for this experiment by hand-pollinating individuals using the breeding design described in the next section.

@@

$$V_P = V_G + V_E$$
We did not have statistical power to estimate nonadditive genetic contributions, therefore we estimated broad-sense ($H^2$) heritability, the fraction of phenotypic variance contributed by all sources of (including dominance and epistasis) genetic variance:

@@

## Estimating genetic variance in germination rate
The full germination-rate model included a fixed effect of population, fixed effect of cohort, a random effect of greenhouse block, and a random effect of parent as either dam or sire to estimate genetic variance. Most quantitative traits are modeled with a Gaussian (i.e. normal) distribution, but this is inappropriate for germination which has a lower bound at 0 and is censused at discrete time points. A Gaussian distribution might be an adequate approximation if the time to germination was longer and more spread out so that the effects of a zero lower bound and discrete sampling interval were inconsequential. However, given the rapid germination rate and small spread in timing for *M. cardinalis*, we used a different approach. Instead, we modeled genetic variation in a continuously distributed latent rate parameter that is measured as a discrete number of days to germination. Time to germination can be modeled similar to other waiting time or survival processes. There are several common waiting-time distributions with a lower bound at zero, but we used the log-normal distribution because unlike some other common distributions (e.g. exponential), the mean and variance of log-normal distribution are separate parameters. Hence, we can model the variance components separate from differences in the mean germination rate. We discretized the distribution using the definite integral of the probability density to calculate a probability mass. Let the probability density with parameters $\theta$ be $f(x|\theta)$. If a seed was censused to have germinated on day $i$, it could have germinated at any time between the previous census on day $t_{i-1}$. The associated probability mass $g(x|\theta)$ is:

@@

Phenotypic clines are often interpreted as evidence for local adaptation but evolutionary forces besides selection can also generate associations between phenotypes and environment [@endler_geographic_1977]. If genotypic selection measured under natural conditions favors local phenotypes, this supports the hypothesis that phenotypic clines are adaptive. Alternatively, failure to detect selection could indicate that nonadaptive evolutionary forces maintain phenotypic variation. We measured the effect of germination rate in the greenhouse, which varies clinally with latitude in *Mimulus cardinalis* [@muir_grow_2017], on early winter survival. Although there was genetic variation in germination rate within and between five populations (Table \ref{tab:focal_pops}; Table \ref{tab:vc_table_germ}; Fig. \ref{fig:mean-traits}a), there was no evidence selection consistently favored local genotypes. We predicted that earlier germination should be favored in the South garden and later germination favored in the North garden. Instead, in both North and South gardens, populations that germinated faster on average also had higher survival, though survival in the North garden was lower than the South overall (Fig. \ref{fig:selection}). Apparent selection for faster germination in both gardens is likely indirect rather than causal. Populations originating from the southern range limit survived more often and germinated faster. Within populations there was no genetic variance in winter survival despite genetic variance in germination rate, indicating that differences in germination rate are probably not the main cause of differences in winter survival. Our results are not consistent with selection on survival maintaining phenotypic clines in germination rate. Rather, the results may indicate a role for nonadaptive evolution or that selection operates on germination rate during other life stages.

@@

## What maintains genetic variation in germination rate?
One possibility is that germination rate measured in the greenhouse is not representative of what occurs in nature. In the field, seeds may use additional cues such as day length or temperature that did not vary in our experiment. We may not be able to measure selection on variation in germination rate unless it occurs in the field. For example, seedlings in the north may require a longer duration of favorable conditions to ensure they do not germinate in late fall or during a brief warm period in early spring. Either scenario might cause them to be exposed to a hard, damaging frost. We may not be able to observe this type of selection without germinating plants in the field at different times of the season. Alternatively, variation may be the result of nonadaptive evolution. *Mimulus cardinalis* demography varies latitudinally in a pattern consistent with an ongoing northward range expansion [@sheth_demographic_2018]. Population expansion can lead to the accumulation of deleterious alleles because of stronger genetic drift [@peischl_accumulation_2013], serial founder events [@slatkin_serial_2012], and maladaptation [@polechova_is_2018]. If selection actually favors faster germination, the slower germination and lower survival of northern populations may both be caused by the accumulation of deleterious genetic variation at the expanding range margins. The current cline could also be a legacy of selection in the recent past which is now less strong or at least not observed during our study [@saccheri_selection_2008].

@@

The reciprocal transplant experiment did not support our hypothesis that local adaptation maintains clinal variation in germination rate in *M. cardinalis*. We cannot exclude the possibility that artificial aspects of our experimental design may have prevented us from measuring selection on germination rate realistically or that selection operates via different components of fitness. It is also possible that climate anomalies during our experiment prevented us from observing historical patterns of selection that led to present-day phenotypic variation. It is plausible that the cline in germination rate and other phenotypes may be caused by nonadaptive forces that increase the frequency of deleterious alleles during range expansion. Studies like ours that combine clines with reciprocal transplants are necessary to determine what evolutionary forces shape range-wide phenotypic variation within species.

### 2021-12-14 ms/ms.tex
rearranged target order
biorxiv

\usepackage{lineno}
\linenumbers

@@

\setstretch{1.5}
\(^{1}\) Department of Botany, University of British Columbia, Vancouver, BC V6T 1Z4, Canada

@@

Manuscript received \_\_\_\_\_\_\_; revision accepted \_\_\_\_\_\_\_.

\emph{short title}: Selection on germination in \emph{Mimulus cardinalis}

@@

\emph{Mimulus cardinalis} (\(=\)\emph{Erythranthe cardinalis} (\protect\hyperlink{ref-lowry_case_2019}{Lowry et al., 2019})) is a perennial forb native to the Western US (California and Oregon). It is predominantly outcrossing, self-compatible, hummingbird-pollinated. We used five focal populations from throughout the geographic range of \emph{M. cardinalis} (Table \ref{tab:focal_pops}). These five focal populations are a subset of those we used previously to identify a cline in germination and other traits (\protect\hyperlink{ref-muir_grow_2017}{Muir and Angert, 2017}). Seeds were collected in the field from mature, undehisced fruits left in open coin envelopes for 2-4 weeks to dry, then stored at room temperature. To control for maternal effects, we grew a large number of field-collected seeds in the greenhouse and generated seed families for this experiment by hand-pollinating individuals using the breeding design described in the next section.

@@

\[V_P = V_G + V_E\]
We did not have statistical power to estimate nonadditive genetic contributions, therefore we made the simplifying operational assumption that all genetic variance is additive. The broad-sense (\(H^2\)) heritability is the fraction of phenotypic variance contributed by additive genetic variance:

@@

The full germination-rate model included a fixed effect of population, fixed effect of cohort, a random effect of greenhouse block, and a random effect of parent as either dam or sire to estimate additive genetic variance. Most quantitative traits are modeled with a Gaussian (i.e.~normal) distribution, but this is inappropriate for germination which has a lower bound at 0 and is censused at discrete time points. A Gaussian distribution might be an adequate approximation if the time to germination was longer and more spread out so that the effects of a zero lower bound and discrete sampling interval were inconsequential. However, given the rapid germination rate and small spread in timing for \emph{M. cardinalis}, we used a different approach. Instead, we modeled genetic variation in a continuously distributed latent rate parameter that is measured as a discrete number of days to germination. Time to germination can be modeled similar to other waiting time or survival processes. There are several common waiting-time distributions with a lower bound at zero, but we used the log-normal distribution because unlike some other common distributions (e.g.~exponential), the mean and variance of log-normal distribution are separate parameters. Hence, we can model the variance components separate from differences in the mean germination rate. We discretized the distribution using the definite integral of the probability density to calculate a probability mass. Let the probability density with parameters \(\theta\) be \(f(x|\theta)\). If a seed was censused to have germinated on day \(i\), it could have germinated at any time between the previous census on day \(t_{i-1}\). The associated probability mass \(g(x|\theta)\) is:

@@

Phenotypic clines are often interpreted as evidence for local adaptation but evolutionary forces besides selection can also generate associations between phenotypes and environment (\protect\hyperlink{ref-endler_geographic_1977}{Endler, 1977}). If genotypic selection measured under natural conditions favors local phenotypes, this supports the hypothesis that phenotypic clines are adaptive. Alternatively, failure to detect selection could indicate that nonadaptive evolutionary forces maintain phenotypic variation. We measured the effect of germination rate in the greenhouse, which varies clinally with latitude in \emph{Mimulus cardinalis} (\protect\hyperlink{ref-muir_grow_2017}{Muir and Angert, 2017}), on early winter survival. Although there was genetic variation in germination rate within and between five populations (Table \ref{tab:focal_pops}; Table \ref{tab:vc_table_germ}; Fig. \ref{fig:mean-traits}a), there was no evidence selection consistently favored local genotypes. We predicted that earlier germination should be favored in the South garden and later germination favored in the North garden. Instead, in both North and South gardens, populations that germinated faster on average also had higher survival, though survival in the North garden was lower than the South overall (Fig. \ref{fig:selection}). Apparent selection for faster germination in both gardens is likely indirect rather than causal. Populations originating from the southern range limit survived more often and germinated faster. Within populations there was no genetic variance in winter survival despite genetic variance in germination rate, indicating that differences in germination rate are probably not the main cause of differences in winter survival. Our results are not consistent with selection on survival maintaining phenotypic clines in germination rate. Rather, the results may indicate a role for nonadaptive evolution in this and possibly other traits.

@@

One possibility is that germination rate measured in the greenhouse is not representative of what occurs in nature. In the field, seeds may use additional cues such as day length or temperature that did not vary in our experiment. We may not be able to measure selection on variation in germination rate unless it occurs in the field. For example, seedlings in the north may require a longer duration of favorable conditions to ensure they do not germinate in late fall or during a brief warm period in early spring. Either scenario might cause them to be exposed to a hard, damaging frost. We may not be able to observe this type of selection without germinating plants in the field at different times of the season. Alternatively, variation may be the result of nonadaptive evolution. \emph{M. cardinalis} has expanded its range northward most likely after the last glacial maximum (\protect\hyperlink{ref-sheth_demographic_2018}{Sheth and Angert, 2018}). Population expansion can lead to the accumulation of deleterious alleles because of stronger genetic drift (\protect\hyperlink{ref-peischl_accumulation_2013}{Peischl et al., 2013}), serial founder events (\protect\hyperlink{ref-slatkin_serial_2012}{Slatkin and Excoffier, 2012}), and maladaptation (\protect\hyperlink{ref-polechova_is_2018}{Polechová, 2018}). If selection actually favors faster germination, the slower germination and lower survival of northern populations may both be caused by the accumulation of deleterious genetic variation at the expanding range margins. The current cline could also be a legacy of selection in the recent past which is now less strong or at least not observed during our study (\protect\hyperlink{ref-saccheri_selection_2008}{Saccheri et al., 2008}).

@@

The reciprocal transplant experiment did not support our hypothesis that local adaptation maintains clinal variation in germination rate in \emph{M. cardinalis}. We cannot exclude the possibility that artificial aspects of our experimental design may have prevented us from measuring selection on germination rate realistically. It is also possible that climate anomalies during our experiment prevented us from observing historical patterns of selection that led to present-day phenotypic variation. It is plausible that the cline in germination rate and other phenotypes may be caused by nonadaptive forces that increase the frequency of deleterious alleles during range expansion. Studies like ours that combine clines with reciprocal transplants are necessary to determine what evolutionary forces shape range-wide phenotypic variation within species.

>>>>

\usepackage{lineno}
% \linenumbers % toggle on for linenumbers

@@

\setstretch{1}
\(^{1}\) Department of Botany, University of British Columbia, Vancouver, BC V6T 1Z4, Canada

@@

@@

\emph{Mimulus cardinalis} (\(=\)\emph{Erythranthe cardinalis} (\protect\hyperlink{ref-lowry_case_2019}{Lowry et al., 2019})) is a perennial forb native to the Western US (California and Oregon). It is predominantly outcrossing, self-compatible, and hummingbird-pollinated. We used five focal populations from throughout the geographic range of \emph{M. cardinalis} (Table \ref{tab:focal_pops}). These five focal populations are a subset of those we used previously to identify a cline in germination and other traits (\protect\hyperlink{ref-muir_grow_2017}{Muir and Angert, 2017}). Seeds were collected in the field from mature, undehisced fruits left in open coin envelopes for 2-4 weeks to dry, then stored at room temperature. To control for maternal effects, we grew a large number of field-collected seeds in the greenhouse and generated seed families for this experiment by hand-pollinating individuals using the breeding design described in the next section.

@@

\[V_P = V_G + V_E\]
We did not have statistical power to estimate nonadditive genetic contributions, therefore we estimated broad-sense (\(H^2\)) heritability, the fraction of phenotypic variance contributed by all sources of (including dominance and epistasis) genetic variance:

@@

The full germination-rate model included a fixed effect of population, fixed effect of cohort, a random effect of greenhouse block, and a random effect of parent as either dam or sire to estimate genetic variance. Most quantitative traits are modeled with a Gaussian (i.e.~normal) distribution, but this is inappropriate for germination which has a lower bound at 0 and is censused at discrete time points. A Gaussian distribution might be an adequate approximation if the time to germination was longer and more spread out so that the effects of a zero lower bound and discrete sampling interval were inconsequential. However, given the rapid germination rate and small spread in timing for \emph{M. cardinalis}, we used a different approach. Instead, we modeled genetic variation in a continuously distributed latent rate parameter that is measured as a discrete number of days to germination. Time to germination can be modeled similar to other waiting time or survival processes. There are several common waiting-time distributions with a lower bound at zero, but we used the log-normal distribution because unlike some other common distributions (e.g.~exponential), the mean and variance of log-normal distribution are separate parameters. Hence, we can model the variance components separate from differences in the mean germination rate. We discretized the distribution using the definite integral of the probability density to calculate a probability mass. Let the probability density with parameters \(\theta\) be \(f(x|\theta)\). If a seed was censused to have germinated on day \(i\), it could have germinated at any time between the previous census on day \(t_{i-1}\). The associated probability mass \(g(x|\theta)\) is:

@@

Phenotypic clines are often interpreted as evidence for local adaptation but evolutionary forces besides selection can also generate associations between phenotypes and environment (\protect\hyperlink{ref-endler_geographic_1977}{Endler, 1977}). If genotypic selection measured under natural conditions favors local phenotypes, this supports the hypothesis that phenotypic clines are adaptive. Alternatively, failure to detect selection could indicate that nonadaptive evolutionary forces maintain phenotypic variation. We measured the effect of germination rate in the greenhouse, which varies clinally with latitude in \emph{Mimulus cardinalis} (\protect\hyperlink{ref-muir_grow_2017}{Muir and Angert, 2017}), on early winter survival. Although there was genetic variation in germination rate within and between five populations (Table \ref{tab:focal_pops}; Table \ref{tab:vc_table_germ}; Fig. \ref{fig:mean-traits}a), there was no evidence selection consistently favored local genotypes. We predicted that earlier germination should be favored in the South garden and later germination favored in the North garden. Instead, in both North and South gardens, populations that germinated faster on average also had higher survival, though survival in the North garden was lower than the South overall (Fig. \ref{fig:selection}). Apparent selection for faster germination in both gardens is likely indirect rather than causal. Populations originating from the southern range limit survived more often and germinated faster. Within populations there was no genetic variance in winter survival despite genetic variance in germination rate, indicating that differences in germination rate are probably not the main cause of differences in winter survival. Our results are not consistent with selection on survival maintaining phenotypic clines in germination rate. Rather, the results may indicate a role for nonadaptive evolution or that selection operates on germination rate during other life stages.

@@

One possibility is that germination rate measured in the greenhouse is not representative of what occurs in nature. In the field, seeds may use additional cues such as day length or temperature that did not vary in our experiment. We may not be able to measure selection on variation in germination rate unless it occurs in the field. For example, seedlings in the north may require a longer duration of favorable conditions to ensure they do not germinate in late fall or during a brief warm period in early spring. Either scenario might cause them to be exposed to a hard, damaging frost. We may not be able to observe this type of selection without germinating plants in the field at different times of the season. Alternatively, variation may be the result of nonadaptive evolution. \emph{Mimulus cardinalis} demography varies latitudinally in a pattern consistent with an ongoing northward range expansion (\protect\hyperlink{ref-sheth_demographic_2018}{Sheth and Angert, 2018}). Population expansion can lead to the accumulation of deleterious alleles because of stronger genetic drift (\protect\hyperlink{ref-peischl_accumulation_2013}{Peischl et al., 2013}), serial founder events (\protect\hyperlink{ref-slatkin_serial_2012}{Slatkin and Excoffier, 2012}), and maladaptation (\protect\hyperlink{ref-polechova_is_2018}{Polechová, 2018}). If selection actually favors faster germination, the slower germination and lower survival of northern populations may both be caused by the accumulation of deleterious genetic variation at the expanding range margins. The current cline could also be a legacy of selection in the recent past which is now less strong or at least not observed during our study (\protect\hyperlink{ref-saccheri_selection_2008}{Saccheri et al., 2008}).

@@

The reciprocal transplant experiment did not support our hypothesis that local adaptation maintains clinal variation in germination rate in \emph{M. cardinalis}. We cannot exclude the possibility that artificial aspects of our experimental design may have prevented us from measuring selection on germination rate realistically or that selection operates via different components of fitness. It is also possible that climate anomalies during our experiment prevented us from observing historical patterns of selection that led to present-day phenotypic variation. It is plausible that the cline in germination rate and other phenotypes may be caused by nonadaptive forces that increase the frequency of deleterious alleles during range expansion. Studies like ours that combine clines with reciprocal transplants are necessary to determine what evolutionary forces shape range-wide phenotypic variation within species.

### 2021-12-14 ms/si.Rmd
biorxiv

---
title: 'Supporting Information'
output:
  bookdown::pdf_document2:
    includes:
      before_body: ../template/doc_prefix.tex
      in_header: ../template/preamble.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2: null
fontsize: 12pt
linestretch: 1.5
link-citations: yes
csl: ../template/annals-of-botany.csl
bibliography: ../ms/mimulus-germination.bib
---

>>>>

---
title: 'Supporting Information'
output:
  bookdown::pdf_document2:
    includes:
      before_body: ../template/doc_prefix.tex
      in_header: ../template/preamble.tex
    keep_tex: yes
    latex_engine: xelatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2: null
fontsize: 12pt
linestretch: 1
link-citations: yes
csl: ../template/american-journal-of-botany.csl
bibliography: ../ms/mimulus-germination.bib
---
